---
title: "luq_streamchem: Stream chemistry for Quebrada Sonadora site (Luquillo LTER)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{luq_stream_chem}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Overview

The `luq_streamchem` data contains a subset of stream flow chemistry data for the Quebrada Sonadora (QS) site within the Espiritu Santo drainage basin and the El Verde Research area of the Luquillo Experimental Forest (LEF). QS is the high elevation site.


```{r setup}
library(lterdatasets)
library(tidyverse)
library(lubridate)
```

# Some cool Data Anlaysis

See: https://www-cambridge-org.proxy.library.ucsb.edu:9443/core/journals/journal-of-tropical-ecology/article/effects-of-hurricane-disturbance-on-stream-water-concentrations-and-fluxes-in-eight-tropical-forest-watersheds-of-the-luquillo-experimental-forest-puerto-rico/2511D4A53DA2C95406014ED75441E77B


```{r}
ggplot(luq_streamchem, aes(x=Sample_Date, y=K)) +
  geom_line( color="#69b3a2") + 
  xlab("") +
  theme_bw() +
  theme(axis.text.x=element_text(angle=60, hjust=1)) +
  labs(title = "Potasium in mg/L") 

```


# How we processes the raw data

`r knitr::spin_child(here::here("data-raw","luq_streamchem_data.R"))`




